Title Goes Here

### 2021-03-30 analysis/paper/paper.Rmd
Agrega unidades en o3-regr-cap
Closes #6
Agrega justificación de ondas zonales (ups anterior)

We used monthly geopotential height, air temperature, ozone mixing ratio, and Total Ozone COlumn (TOC) at 2.5\degree\ longitude by 2.5\degree\ latitude of horizontal resolution and 37 vertical isobaric levels from ERA5 [@era5] for the period 1979 to 2019. We restricted most of our analysis to the post-satellite era to avoid any confounding factors arising from the incorporation of satellite observations, but we also used the preliminary back extension of ERA5 from 1950 to 1978 [@era5be] to look at long-term trends. We derived streamfunction at 200 hPa from ERA5 vorticity using the FORTRAN subroutine FISHPACK [@fishpack] and computed horizontal wave activity fluxes following @plumb1985. For precipitation data we used monthly data from the CPC Merged Analysis of Precipitation [@cmap], with a 2.5\degree\ resolution in latitude and longitude. This rainfall gridded dataset is based on information from different sources such as rain gauge observations, satellite inferred estimations and the NCEP-NCAR reanalysis, and it is available since 1979 to present.

@@

@@

\textcolor{red}{Aclarar qué a lo largo del trabajo se utilizan los datos de primavera y cómo se calcula eso. Tambień creo que acá se podría aclarar que el análisis se concentra en dos niveles para representar la estratósfera y la troposféra alta}

We computed the amplitude and phase of the zonal wave 1 by averaging variables (temperature, geopotential height, ozone mixing ratio and Total Ozone Column) `r knitr::combine_words(LatLabel(o3wave_lats))` for each Spring and computing the Fourier spectrum.

@@

(ref:o3-regr-cap) Regression coefficients of SON mean Total Ozone Column anomalies onto the real (a) and imaginary (b) components of the cEOF1. On contours, the mean zonal anomaly of Total OZone Column (negative contours in dashed lines). ¿Units? For  the 1979 -- 2019 period.

>>>>

We used monthly geopotential height, air temperature, ozone mixing ratio, and Total Ozone Column (TOC) at 2.5\degree\ longitude by 2.5\degree\ latitude of horizontal resolution and 37 vertical isobaric levels from ERA5 [@era5] for the period 1979 to 2019. We restricted most of our analysis to the post-satellite era to avoid any confounding factors arising from the incorporation of satellite observations, but we also used the preliminary back extension of ERA5 from 1950 to 1978 [@era5be] to look at long-term trends. We derived streamfunction at 200 hPa from ERA5 vorticity using the FORTRAN subroutine FISHPACK [@fishpack] and computed horizontal wave activity fluxes following @plumb1985. For precipitation data we used monthly data from the CPC Merged Analysis of Precipitation [@cmap], with a 2.5\degree\ resolution in latitude and longitude. This rainfall gridded dataset is based on information from different sources such as rain gauge observations, satellite inferred estimations and the NCEP-NCAR reanalysis, and it is available since 1979 to present.

@@

We restrict our study to  the September-October-November (SON) trimester. For that, we use seasonal means, averaging monthly values weighted by the number of days in each  month. We also use 200 hPa to represent the high troposphere and 50 hPa to represent the lower stratosphere.

@@

@@

(ref:o3-regr-cap) Regression coefficients of SON mean Total Ozone Column anomalies onto the real (a) and imaginary (b) components of the cEOF1. On contours, the mean zonal anomaly of Total OZone Column (negative contours in dashed lines, Dobson Units). For  the 1979 -- 2019 period.
